---
title: "What type of Students are responding to purple posts?"
author: "Santosh Jnawali ,  Hussam Taj"
date: "10/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
master <- read.csv("C:/Users/Hussam Taj/Desktop/Fall 2019/STAT 300/ChangeLab Purple Posts/PurplePostMaster.csv")
replies <- read.csv("C:/Users/Hussam Taj/Desktop/Fall 2019/STAT 300/ChangeLab Purple Posts/PurplePostReplies.csv")
StudentStaticInformation <- read.csv("C:/Users/Hussam Taj/Desktop/Fall 2019/STAT 300/ChangeLab Purple Posts/StudentStaticInformation.csv")
StudentTermInformation <- read.csv("C:/Users/Hussam Taj/Desktop/Fall 2019/STAT 300/ChangeLab Purple Posts/StudentTermInformation.csv")

```


##What kind of students are responding to the purple post based on the different variable?

Need to know the total participants, 
Replied puple post no. Participant Id, 
What type of replies are characterized by different variable , 
Variable may be Race, Geography , etc.


##In order to know the exact number of student replying the purple post , we are looking at the participant ID from replied dataset matching to the student Annon ID of Master dataset . 
```{r}
replied_participant<- unique(replies$ParticipantId)

Student_annon<- unique(master$StudentAnonId)
```

##Counting the number of student replying to the purple post 

```{r}
count<-sum(Student_annon %in% replied_participant)
count
```


##Total number of unique student participants
```{r}
length(unique(master$StudentAnonId))

```

## Proportion of student replying to the purple post 
```{r}
336/2657
```
12.64% of the student who are issued purple post are replying to them. 

## Finding the information of student replying purple post. 

```{r}
replied_student_annonID<-intersect(replied_participant, Student_annon)
```

```{r}
reply_Indicator<-StudentStaticInformation%>%
  mutate(Reply=if_else(AnonStudentId %in% replied_student_annonID,1,0))
```

##Exploratory Data analysis 
Bar plot of the student replying to purple post and not replying to purple post .
```{r}

plot1<-ggplot(data = reply_Indicator) + 
  geom_bar(mapping = aes(x =factor(Reply)),width = 0.5)
plot1
```
Here, O indicates the students not replying purple post and 1 indicates student replying purple post.

Looking at the plot based on the Geographic region

```{r}
ggplot(data = reply_Indicator) + 
  geom_bar(mapping = aes(x =factor(Reply),fill=GeographicRegion),width = 0.5)

```


```{r}
ggplot(data = reply_Indicator) + 
  geom_bar(mapping = aes(x =factor(Reply),fill=International),width = 0.5)
```
```{r}
ggplot(data = reply_Indicator) + 
  geom_bar(mapping = aes(x =factor(Reply),fill=CurrentStatus),width = 0.5)
```
##separate unique student and their geographic and other information.
##make a different dataset includeing everyinformation with a variable replied or not. 
##Make several scatterplot, box plot using the available variables.

```{r}
new_replyr<- StudentTermInformation%>%
  mutate(Reply=if_else(StudentTermInformation$StudentAnonId %in% replied_student_annonID,1,0))
```



##Filtering unique student ID information from the dataset studentTermInformation:

```{r}
unique_info<-subset(new_replyr,!duplicated(StudentAnonId))
```


















